---
title: Practice on the dplyr package
author: Rodolfo Lerma
output: Questions/Answers
  html_notebook
---

###Importing Data
- To import a csv file in R, we use the read.csv funcion.
- The data file is available on Canvas as well as on Kaggle
- Before importing, please make sure your working directory is set to the folder which holds the avocado.csv file is. Else, you will need to provide the address of the avocado.csv file.
```{r}
avocado<-read.csv("avocado.csv", header=TRUE)
```


###Look at the data structure
```{r message=FALSE}
library(dplyr)
library(tidyr)
str(avocado)
```

```{r}
head(avocado)
```

###Select all rows where AveragePrice of Avocado is greater than 1.6 
```{r}
#write your code here
filter(avocado,AveragePrice > 1.6)
```
###Report whether organic avocado sells more in terms of Total.Volume than conventional avocado
```{r}
#write your code here
test <- group_by(avocado,type)
summarize(test, sum(Total.Volume))
```

###Report the regions where organic avocado sells more then conventional avocado in terms of Total.Volume
```{r}
avocado_summary <- avocado %>% 
  group_by(region, type) %>% 
  summarize(TotalVolume = sum(Total.Volume), .groups = 'drop') %>% 
  pivot_wider(names_from = type, values_from = TotalVolume) %>% 
  filter(organic > conventional)

avocado_summary
```

###Report the Average Total.Volume by AveragePrice quantiles of 7 for conventional and organic avacado  
```{r}
avocado %>% 
  group_by(type) %>% 
  mutate(PriceQuantile = ntile(AveragePrice, 7)) %>% 
  group_by(type, PriceQuantile) %>% 
  summarize(AvgTotalVolume = mean(Total.Volume))

```
###Report in which regions with highest number of bags of avocado sold by bag size and year.
```{r}
avocado %>% 
  mutate(Year = as.factor(format(as.Date(Date, "%Y-%m-%d"), "%Y"))) %>% 
  group_by(region, Year) %>% 
  summarize(
    SmallBagsTotal = sum(Small.Bags),
    LargeBagsTotal = sum(Large.Bags),
    XLargeBagsTotal = sum(XLarge.Bags)) %>% 
  pivot_longer(
    cols = -c(region, Year),
    names_to = "BagSize",
    values_to = "TotalBags") %>% 
  arrange(desc(TotalBags))
```




